\documentclass[12pt]{article}

\input{preamble}

\begin{document}

\large \textbf{Reader Report} \\
Reading: Title (Author, Year) \\
Name (Uni) \\
\today

\vspace{0.1in}

\normalsize

\section{Abstract}


\section{Introduction}
Venture capitalist and startup founders have been following two simple rules for decades - The success of startup relies on some irreplaceable talents of founders and the funding from large and prestigious VC funds.
To which extent are these success luck, and under which circumstances are these belief true remains an untold story even within the industry.

There are two widely believed hypothesis in the startup and venture capital industry. One is that changing a startup's CEO would be devastating, and the second is that being invested by large funds will more likely lead to success. While startup founders and investors held on to these believe, it is surprising that there are no research article or even commercial reports answering these two hypothesis. This is perhaps due to the lack of data and proper analytical tools for the private sector, letting alone the diversity of startups in recent year.

Given the availability of data in the private sector, we wish to test these two hypothesis using causal inference methods, and natural language processing tools.

We also encounter several difficulties. First, matching is inherently hard in the startup space. Perhaps because of the slow introduction of academic results into the business world, some researchers rely on TF-iDF

\section{Methodology}





\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
